Designing Large-Scale Imaging Surveys for a Retrospective Relative Photometric Calibration

### 2012-04-15 paper/self_calibration_I.tex
paper: remove reference to code for ArXiv upload
minor changes following reviewer comments

\subsection{A Single Exposure}
\label{sec:single_exposure}
With a telescope pointing $(\alpha, \beta)$ and camera orientation $\theta$, we find the focal plane positions of the sources on the synthetic sky that fall within the instrument's field-of-view. In our simulations, we use a large instrument field-of-view of $0.76~ \text{deg} \times 0.72~\text{deg}$; a size consistent with the next generation of large survey imagers. An example of a single pointing exposure is shown in Figure \ref{fig:single_image}.

@@

\subsection{Fitting the Instrument Response Model}
To introduce a realistic level of ignorance into the simulations, we use the self-calibration procedure to fit a model that is \textit{incomplete} in two ways. Firstly, the \textit{fitted} instrument response is modeled as an eighth order polynomial, and not the second order polynomial superimposed with sine and cosine contributions used to model the \textit{true} instrument response. Secondly, the assumed measurement uncertainty variances do not include the additional random measurement error $\epsilon_{i}$ introduced in Subsection \ref{sec:noise}. We 
We therefore fit for the following, incomplete measurement model:
\begin{eqnarray*}
c_i = f(\vec{x_i} | \vec{q}) \, s_{k} + e_{i} \quad ,
\end{eqnarray*}
where $c_i$ is the recorded count rate, $f(\vec{x_i} | \vec{q})$ is the fitted instrument response model at a focal plane position $\vec{x}_i$, $\vec{q}$ is a vector parameterizing the eighth order polynomial instrument response model, $s_k$ is the model source flux estimate and the error $e_i$ is drawn from the Normal Distribution $N(e|0,{\sigma_i}^2)$, such that
\begin{eqnarray*}
\sigma_{{i}}^{2} = \delta^{2} + \eta^{2}\, c^{2}_i \quad ,
\end{eqnarray*} 
where $\delta$ and $\eta$ are the parameters set by the instrument's $10\upsigma$ detection and the S/N $<500$ limits. The $\epsilon_i$ error contribution is intentionally not included in order to simulate systematic problems with the instrument noise model.

@@

\subsection{Survey Description}
We label the four survey strategies -- which all cover the same patch of sky -- with the letters A to D. These survey strategies are summarized in Table \ref{tab:simple_surveys} and are shown in Figure \ref{fig:simple_surveys}. Strategy A is the simplest strategy; the target field is regularly tiled with small overlaps between adjacent pointings ($\sim 5$~percent and $\sim 8$~percent in the camera pointing directions $\alpha$ and $\beta$ respectively). The pointings in the 12 passes over the same field are exactly aligned. Survey B is the same as A, but with each pass over the target field the orientation of the telescope is rotated by $30^\circ$. Survey C is more complex. The first pass over the field is the same as in Survey A, with $12 \times 12$ pointings. In the next pass, one of the pointings in the $\alpha$ direction is removed and one is added in the $\beta$ and the pointings are respaced uniformly, so the resultant pointing grid is $13 \times 11$. In the third pass over the field this change is reversed and the field is measured on a $11 \times 13$ grid. These three passes are then repeated four times. The pointing positions in Survey D are quasi-random: the pointings are the same as with Survey A, but each has a random offset within [-0.35,0.35)~deg applied in both the $\alpha$ and $\beta$ directions. By fixing the pointings within these $0.7~\text{deg} \times 0.7~\text{deg}$ boxes, we ensure that the quasi random strategy has a uniform coverage of the field; that is, the fluctuations in coverage are less than they would be in a Poisson (totally random) process. The orientations of the pointings in Survey D are completely random.

@@

All of the code used in this paper is publicly available at
\url{http://github.com/davidwhogg/SelfCalibration/}~.

>>>>

\subsection{A Single Exposure}
\label{sec:single_exposure}
With a telescope pointing $(\alpha, \beta)$ and camera orientation $\theta$, we find the focal plane positions of the sources on the synthetic sky that fall within the instrument's field-of-view. In our simulations, we use a large instrument field-of-view of $0.76~ \text{deg} \times 0.72~\text{deg}$; a size consistent with current large survey imagers. An example of a single pointing exposure is shown in Figure \ref{fig:single_image}.

@@

\subsection{Fitting the Instrument Response Model}
To introduce a realistic level of ignorance into the simulations, we use the self-calibration procedure to fit a model that is \textit{incomplete} in two ways. Firstly, the \textit{fitted} instrument response is modeled as an eighth order polynomial, and not the second order polynomial superimposed with sine and cosine contributions used to model the \textit{true} instrument response. Secondly, the assumed measurement uncertainty variances do not include the additional random measurement error $\epsilon_{i}$ introduced in Subsection \ref{sec:noise}. We therefore fit for the following, incomplete measurement model:
\begin{eqnarray*}
c_i = f(\vec{x_i} | \vec{q}) \, s_{k} + e_{i} \quad ,
\end{eqnarray*}
where $c_i$ is the recorded count rate, $f(\vec{x_i} | \vec{q})$ is the fitted instrument response model at a focal plane position $\vec{x}_i$, $\vec{q}$ is a vector parameterizing the eighth order polynomial instrument response model, $s_k$ is the model source flux estimate and the error $e_i$ is drawn from the Normal Distribution $N(e|0,{\sigma_i}^2)$, such that
\begin{eqnarray*}
\sigma_{{i}}^{2} = \delta^{2} + \eta^{2}\, c^{2}_i \quad ,
\end{eqnarray*} 
where $\delta$ and $\eta$ are the parameters set by the instrument's $10\upsigma$ detection and the S/N $<500$ limits. The $\epsilon_i$ error contribution is intentionally not included in order to simulate systematic problems with the instrument noise model.

@@

\subsection{Survey Description}
We label the four survey strategies -- which all cover the same 64~deg$^2$ patch of sky -- with the letters A to D. These survey strategies are summarized in Table \ref{tab:simple_surveys} and are shown in Figure \ref{fig:simple_surveys}. Strategy A is the simplest strategy; the target field is regularly tiled with small overlaps between adjacent pointings ($\sim 5$~percent and $\sim 8$~percent in the camera pointing directions $\alpha$ and $\beta$ respectively). The pointings in the 12 passes over the same field are exactly aligned. Survey B is the same as A, but with each pass over the target field the orientation of the telescope is rotated by $30^\circ$. Survey C is more complex. The first pass over the field is the same as in Survey A, with $12 \times 12$ pointings. In the next pass, one of the pointings in the $\alpha$ direction is removed and one is added in the $\beta$ and the pointings are respaced uniformly, so the resultant pointing grid is $13 \times 11$. In the third pass over the field this change is reversed and the field is measured on a $11 \times 13$ grid. These three passes are then repeated four times. The pointing positions in Survey D are quasi-random: the pointings are the same as with Survey A, but each has a random offset within [-0.35,0.35)~deg applied in both the $\alpha$ and $\beta$ directions. By fixing the pointings within these $0.7~\text{deg} \times 0.7~\text{deg}$ boxes, we ensure that the quasi random strategy has a uniform coverage of the field; that is, the fluctuations in coverage are less than they would be in a Poisson (totally random) process. The orientations of the pointings in Survey D are completely random.

@@

%All of the code used in this paper is publicly available at \url{http://github.com/davidwhogg/SelfCalibration/}~.
